### 2021-07-17 chapters/1_abstract.tex
wip until now

\documentclass[../main]{subfiles}
\begin{document}
\chapter*{Abstract}
Software testing is a crucial part of the software engineering process. 
A part of software testing is building test suites which contain unit tests.
These unit tests are written by developers. 
As projects grow the test suite grows along.
Maintaining and monitoring these test suites is important as they influence the cost of maintenance.
For example, a project with a smaller test suite may have a higher maintenance cost as the effect of change has to be measured manually, which can be a time consuming process.
Monitoring the quality of test code has shown that tests with lower quality lead to more defect-prone production code.
A technique to measure the quality of test code is by measuring the test effectiveness.
\newline
Measuring the effectiveness of test suites detecting faults is part of the monitoring process.
A technique to measure the test effectiveness is mutation testing.
Mutation testing is a computationally expensive technique that requires the ability to run tests.
Different techniques have been proposed to reduce the cost of mutation testing.
One of these techniques is the clustering of mutants.
By clustering mutants we can execute less mutants to reduce the cost.
\newline
Our research consists of two parts in which we cluster the mutants.
The first part consists of a white box approach and the second part of a black box approach.
We conducted a state of the art comparison between three mutation testing tools for Java.
Based on this research we selected a mutation testing tool to use in our experiments.
\newline
We identified characteristics to represent the mutants so that we can cluster them.
For our white box approach we used hierarchical clustering and for the black box approach we trained the \acrlong{fcm} model.
We calculated a weighted mutation score and compared this with the mutation score of a full set of mutants executed.
Results show that with hierarchical clustering we can reduce the amount of mutants executed while maintaining the effectiveness.
The clusters generated by the machine learning model were less accurate and showed a significant decrease in effectiveness.
The machine learning model did not perform as well as the hierarchical clustering.
However, more can be done by experimenting with different approaches in finding the right parameters for the \acrlong{fcm} algorithm. 
\end{document}

>>>>

\documentclass[../main]{subfiles}
\begin{document}
\chapter*{Abstract}
Software testing is a crucial part of the software engineering process. 
A part of software testing is building test suites which contain unit tests.
These unit tests are written by developers. 
As projects grow the test suite grows along.
Maintaining and monitoring these test suites is important as they influence the cost of maintenance.
For example, a project with a smaller test suite may have a higher maintenance cost as the effect of change has to be measured manually, which can be a time consuming process.
Monitoring the quality of test code has shown that tests with lower quality lead to more defect-prone production code.
A technique to measure the quality of test code is by measuring the test effectiveness.
\newline
Measuring the effectiveness of test suites detecting faults is part of the monitoring process.
A technique to measure the test effectiveness is mutation testing.
Mutation testing is a computationally expensive technique that requires the ability to run tests.
Different techniques have been proposed to reduce the cost of mutation testing.
One of these techniques is the clustering of mutants.
By clustering mutants we can execute less mutants to reduce the cost.
\newline
Our research consists of two parts in which we cluster the mutants.
The first part consists of a white box approach and the second part of a black box approach.
We conducted a state of the art comparison between three mutation testing tools for Java.
Based on this research we selected a mutation testing tool to use in our research.
\newline
We identified characteristics to represent the mutants such that we can cluster them.
For our white box approach we used hierarchical clustering and for our black box approach we trained the \acrlong{fcm} model.
We calculated a weighted mutation score and compared this with the mutation score of a full set of mutants executed.
Results show that with hierarchical clustering we can reduce the amount of mutants executed while maintaining the effectiveness.
The clusters generated by the machine learning model were less accurate and showed a significant decrease in effectiveness.
The machine learning model did not perform as well as the hierarchical clustering.
However, more can be done by researching different approaches for training the \acrshort{fcm} model and finding the right parameters. 
\end{document}

### 2021-07-17 chapters/9_discussion.tex
wip until now

\section{RQ 2: Training a machine learning model and clustering mutant characteristics}
The maximum deviation from the original mutation score, for all variants(with and without Levenshtein distance characteristic) of the experiment, is above the statistical threshold.
The biggest deviation measured is 22.39\%.
This is significantly higher than the biggest deviation measured in the first experiment.
56\% of the results of both variants had a deviation in mutation score bigger than 5\%.
\begin{finding}
Our hypothesis does not hold for the clustering the mutants with the \acrshort{fcm} model trained in our experiment.
\end{finding}
We observe that the number of clusters does not have an obvious relation to the total amount of mutants. 
This is expected as the subtractive clustering does not look at the total amount of data points(mutants) but to the contents(characteristics) of the data points.
The number of clusters compared to the that of the hierarchical clustering is significantly lower.
While we do not know the exact clusters centroids the subtractive model calculated, a low number of clusters indicates close relationships between certain mutants.
\begin{finding}
The mutants represented as characteristics in our data set per project have, according to the subtractive clustering model, close relationships to certain other mutants in the same data set.
\end{finding}
We observe that the minimum lowest minimum cluster accuracy measured over all variants and projects is 50.54\% with and average of 62\%. 
This is higher than the minimum of the hierarchical clustering.
This means that in all project there was not one cluster that was evenly divided.
While the minimum accuracy was higher, the maximum accuracy was lower compared to the maximum accuracy of the hierarchical clustering results.
The highest accuracy measured over all variants and projects is 97.80\% with an average of 83.79\%
This means that in all project there was not one cluster that consisted of only survived or killed mutants.
\begin{finding}
The overall accuracy of the clusters generated by the \acrshort{fcm} model in both variants is lower compared to that of the hierarchical clustering.
\end{finding}
When we compare the accuracy per project between the \acrshort{fcm} model and hierarchical clustering we can observe that the lower accuracy of the \acrshort{fcm} model clusters have a higher impact on the deviation in mutation score.
This is caused by the relatively low number of clusters.
One cluster contains more mutants which results in a bigger weight per cluster.
\begin{finding}
The inaccuracy of clusters has a bigger impact on mutation score when the number of clusters is lower.
\end{finding}

\section{Application}
The application of our research is limited to all software projects written in the language Java and the requirements of PIT\cite{pit}.
We can repeat our experiment for every java project that can be run by PIT.
The scope of the research done in the domain of mutation clustering(Chapter \ref{ch:related_work}) is a subset of the scope in our research.
With our research it is possible to cluster all the mutants used in other related research.
The extraction of mutants is build within the PIT plugin system which is a plug and play system.
Applying our research can be done in three steps.
The first step is to run PIT with the plugin to gather the characteristics.
Gathering the characteristics does not take more than a few minutes depending on the number of mutants generated.
The plugin also makes sure PIT exits without executing mutants after gathering the characteristics.
The second step is to run the script for either the \acrshort{fcm} model or the hierarchical clustering.
The last step is to run PIT again with the plugin to filter the mutants based on the results of the clustering.
It is possible to build all these steps into a DevOps pipeline to automate the process. 
The plugins and scripts needed for these steps are available in the code repository on Github\cite{rbasarat-repo}.

>>>>

\section{RQ 2: Training a machine learning model and clustering mutant characteristics}
The maximum deviation from the original mutation score, for all variants(with and without Levenshtein distance characteristic) of the experiment, is above the statistical threshold.
The biggest deviation measured is 22.39\%.
This is significantly higher than the biggest deviation measured in the first experiment.
56\% of the results of both variants had a deviation in mutation score bigger than 5\%.
Our hypothesis does not hold for the clustering the mutants with the \acrshort{fcm} model trained in our experiment.
We observe that the number of clusters does not have an obvious relation to the total amount of mutants. 
This is expected as the subtractive clustering does not look at the total amount of data points(mutants) but to the contents(characteristics) of the data points.
The number of clusters compared to the that of the hierarchical clustering is significantly lower.
While we do not know the exact clusters centroids the subtractive model calculated, a low number of clusters indicates close relationships between certain mutants.
The mutants represented as characteristics in our data set per project have, according to the subtractive clustering model, close relationships to certain other mutants in the same data set.
We observe that the minimum lowest minimum cluster accuracy measured over all variants and projects is 50.54\% with and average of 62\%. 
This is higher than the minimum of the hierarchical clustering.
This means that in all project there was not one cluster that was evenly divided.
While the minimum accuracy was higher, the maximum accuracy was lower compared to the maximum accuracy of the hierarchical clustering results.
The highest accuracy measured over all variants and projects is 97.80\% with an average of 83.79\%
This means that in all project there was not one cluster that consisted of only survived or killed mutants.
The overall accuracy of the clusters generated by the \acrshort{fcm} model in both variants is lower compared to that of the hierarchical clustering.
When we compare the accuracy per project between the \acrshort{fcm} model and hierarchical clustering we can observe that the lower accuracy of the \acrshort{fcm} model clusters have a higher impact on the deviation in mutation score.
This is caused by the relatively low number of clusters.
One cluster contains more mutants which results in a bigger weight per cluster.
The inaccuracy of clusters has a bigger impact on mutation score when the number of clusters is lower.
\section{Application}
The application of our research is limited to all software projects written in the language Java and the requirements of PIT\cite{pit}.
We can repeat our experiment for every java project that can be run by PIT.
The scope of the research done in the domain of mutation clustering(Chapter \ref{ch:related_work}) is a subset of the scope in our research.
With our research it is possible to cluster all the mutants used in other related research.
The extraction of mutants is build within the PIT plugin system which is a plug and play system.
Applying our research can be done in three steps.
The first step is to run PIT with the plugin to gather the characteristics.
Gathering the characteristics does not take more than a few minutes depending on the number of mutants generated.
The plugin also makes sure PIT exits without executing mutants after gathering the characteristics.
The second step is to run the script for either the \acrshort{fcm} model or the hierarchical clustering.
The last step is to run PIT again with the plugin to filter the mutants based on the results of the clustering.
It is possible to build all these steps into a DevOps pipeline to automate the process. 
The plugins and scripts needed for these steps are available in the code repository on Github\cite{rbasarat-repo}.
